Variance in scarid grazing behavior across Caribbean reef sites

### 2019-04-24 r/Analysis.Rmd
4/24

# feeding rates
leveneTest(fr ~ site, data = sum_id_stop) # variances are slightly heteroskedastic, p ~ 0.04, use KW instead of ANOVA
kruskal.test(fr ~ site, data = sum_id_stop) # significant variation across groups

leveneTest(fr ~ site, data = sum_id_qup) # variances are homogenous, p > 0.05, can use ANOVA
aov_fr_qup <- aov(fr ~ site, data = sum_id_qup) 
summary.aov(aov_fr_qup) # significant variation across sites

# bite rates
leveneTest(br ~ site, data = sum_id_stop) # variances are heteroskedastic, p < 0.05
kruskal.test(br ~ site, data = sum_id_stop) # no significant variation across groups

leveneTest(br ~ site, data = sum_id_qup) # variances are are heteroskedastic, p < 0.05
kruskal.test(br ~ site, data = sum_id_qup) # no significant variation

# time spent feeding
leveneTest(g_frac ~ site, data = sum_id_stop) # variances are homogenous, p > 0.05
aov_g_frac_qup <- aov(g_frac ~ site, data = sum_id_stop) 
summary.aov(aov_g_frac_qup) # significant variation across sites

leveneTest(g_frac ~ site, data = sum_id_qup) # variances are homogenous, p > 0.05
aov_g_frac_qup <- aov(g_frac ~ site, data = sum_id_qup) 
summary.aov(aov_g_frac_qup) # significant variation across sites

# foray length
leveneTest(for_bites ~ site, data = sum_id_stop) # variances are homogenous, p > 0.05
aov_for_bites_stop <- aov(for_bites ~ site, data = sum_id_stop) 
summary.aov(aov_for_bites_stop) # significant variation across sites

leveneTest(for_bites ~ site, data = sum_id_qup) # variances are homogenous, p > 0.05
aov_for_bites_qup <- aov(for_bites ~ site, data = sum_id_qup) 
summary.aov(aov_for_bites_qup) # significant variation across sites

>>>>

# feeding rates
leveneTest(fr ~ site, data = sum_id_stop) # variances are slightly heteroskedastic, p ~ 0.04, use KW instead of ANOVA
kruskal.test(fr ~ site, data = sum_id_stop) # significant variation across sites, p < 0.001

leveneTest(fr ~ site, data = sum_id_qup) # variances are homogenous, p > 0.05, can use ANOVA
aov_fr_qup <- aov(fr ~ site, data = sum_id_qup) 
summary.aov(aov_fr_qup) # significant variation across sites, p < 0.001

# bite rates
leveneTest(br ~ site, data = sum_id_stop) # variances are heteroskedastic, p < 0.05
kruskal.test(br ~ site, data = sum_id_stop) # no significant variation, p > 0.5

leveneTest(br ~ site, data = sum_id_qup) # variances are are heteroskedastic, p < 0.05
kruskal.test(br ~ site, data = sum_id_qup) # no significant variation, p > 0.5

# time spent feeding
leveneTest(g_frac ~ site, data = sum_id_stop) # variances are homogenous, p > 0.05
aov_g_frac_qup <- aov(g_frac ~ site, data = sum_id_stop) 
summary.aov(aov_g_frac_qup) # significant variation across sites, p < 0.001

leveneTest(g_frac ~ site, data = sum_id_qup) # variances are homogenous, p > 0.05
aov_g_frac_qup <- aov(g_frac ~ site, data = sum_id_qup) 
summary.aov(aov_g_frac_qup) # significant variation across sites, p < 0.001

# foray length
leveneTest(for_bites ~ site, data = sum_id_stop) # variances are homogenous, p > 0.05
aov_for_bites_stop <- aov(for_bites ~ site, data = sum_id_stop) 
summary.aov(aov_for_bites_stop) # significant variation across sites, p < 0.001

leveneTest(for_bites ~ site, data = sum_id_qup) # variances are homogenous, p > 0.05
aov_for_bites_qup <- aov(for_bites ~ site, data = sum_id_qup) 
summary.aov(aov_for_bites_qup) # significant variation across sites, p < 0.001

### 2019-04-24 r/Ch2 outline_V3.Rmd
4/24

grid.arrange(left = "Feeding rate (bites/min.)",
  arrangeGrob(fr_q1, fr_q3, fr_q4, fr_q5, fr_q7, ncol=5, right = label_vet),
  arrangeGrob(fr_s1, fr_s3, fr_s4, fr_s5, fr_s7, ncol=5, right = label_vir), 
  nrow=2, heights = c(1,1.2))

@@

grid.arrange(
  arrangeGrob(vg_qup, vg_stop, ncol=2), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1), heights = c(1))

@@

```{r, eval = F}
ggplot(filter(sum_ssp_vg, species_code != "rbp" & phase == "i"), aes(x = fr_mean, y = vg_mean)) +
  geom_point(shape=18) +
  facet_grid(~species) +
  labs(y = "Grazing impact (cm3/hr)",
       x = "Average feeding rate (bites/min)"
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        )
```

@@

autoplot(pca_pred, data = sum_site, colour = 'island',
         loadings = T, loadings.colour = 'gray',
         loadings.label = T, loadings.label.size = 3, loadings.label.colour = 'black',
            loadings.label.repel = T) +
    scale_color_brewer(palette = "Blues") +
    theme_bw() +
    theme(legend.title = element_blank())
ggsave(here("figs/pca_pred.png"))

@@

```{r, echo=F, message=F}
kable(gtab_fr[1:4, ])
plot(gamm3$gam,pages=1)
```

>>>>

@@

@@

```{r, eval = F, echo = F, message = F}
ggplot(filter(sum_ssp_vg, species_code != "rbp" & phase == "i"), aes(x = fr_mean, y = vg_mean)) +
  geom_point(shape=18) +
  facet_grid(~species) +
  labs(y = "Grazing impact (cm3/hr)",
       x = "Average feeding rate (bites/min)"
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        )
```

@@

autoplot(pca_pred, data = sum_site, shape = 'island', colour = 'island',
         loadings = T, loadings.colour = 'gray',
         loadings.label = T, loadings.label.size = 3, loadings.label.colour = 'black',
            loadings.label.repel = T) +
    scale_color_manual(values = c("cadetblue3","cadetblue3","cadetblue3")) +
    theme_bw() +
    theme(legend.title = element_blank())
ggsave(here("figs/pca_pred.png"), width = 8, height = 5)

@@

```{r, echo=F, message=F}
kable(gtab_fr[1:4, ])
plot(gamm10$gam,pages=1)
```
